The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-09-06 figures/origin_mode.tex
modify
改版

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
circle/.style={
rectangle,minimum size=1em,rounded corners=0.5em,
draw=black
}
]
\matrix[row sep=0.5em,column sep=2em] {
% First row:
\node (order) {Demander};& \node (task) [square]{Publish Tasks}; &  & \node (select) [square]{Selection}; & & &  \node (finish) {Product}; \\
\node (start1) {}; & & & & & & \node (stop1) {}; \\
\node (plt) {Platform} ; & &  \node (tb) [square] {Task Hub} ; & \node (candidate) [square] {Resource Candidates} ; & \node (coop) [square] {Cooperate Resources}; & \node (combine) [square] {Task Assembly};\\
\node (start2) {}; & & & & & & \node (stop2) {}; & \\
\node (provider) {Provider};  & \node (resource) [square]{Provide Resources}; & \node (response) [square] {Response Task}; & \node (add) [square]{Add to Candidates}; & \node (match) [square]{Assign Task}; & \node (process) [square] {Process Task Part};  &\\
};
\draw[dotted,thick] (start1.west) -- (stop1.east) (start2.west) -- (stop2.east);
\path[->,dashed] (task.east) edge (tb.north) (tb) edge (response) (add) edge (candidate) (candidate) edge (select) (match) edge (coop) (coop.east) edge (process.west);
\path[->] (response) edge (add) (select.east) edge (match.west) (process) edge (combine) (combine.north) edge (finish.west);
% \path (order) edge[->] (task) (task) edge[->] (match) (match) edge[->] (coord) (coord) edge[->] (process) (process) edge[->] (finish) (provider) edge[->] (resource) (resource) edge[->] (match);
\end{tikzpicture}

>>>>

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
circle/.style={
rectangle,minimum size=1em,rounded corners=0.5em,
draw=black
}
]
\matrix[row sep=0.5em,column sep=2em] {
% First row:
\node (order) {Demander};& \node (task) [square]{Publish Orders}; &  & \node (select) [square]{Selection}; & & &  \node (finish) {Product}; \\
\node (start1) {}; & & & & & & \node (stop1) {}; \\
\node (plt) {Platform} ; & &  \node (tb) [square] {Task Hub} ; & \node (candidate) [square] {Resource Candidates} ; & \node (coop) [square] {Cooperate Resources}; & \node (combine) [square] {Task Assembly};\\
\node (start2) {}; & & & & & & \node (stop2) {}; & \\
\node (provider) {Provider};  & \node (resource) [square]{Provide Resources}; & \node (response) [square] {Response for Task}; & \node (add) [square]{Add to Candidates}; & \node (match) [square]{Assign Task}; & \node (process) [square] {Processing Task-part};  &\\
};
\draw[dotted,thick] (start1.west) -- (stop1.east) (start2.west) -- (stop2.east);
\path[->,dashed] (task.east) edge (tb.north) (tb) edge (response) (add) edge (candidate) (candidate) edge (select) (match) edge (coop) (coop.east) edge (process.west);
\path[->] (response) edge (add) (select.east) edge (match.west) (process) edge (combine) (combine.north) edge (finish.west);
% \path (order) edge[->] (task) (task) edge[->] (match) (match) edge[->] (coord) (coord) edge[->] (process) (process) edge[->] (finish) (provider) edge[->] (resource) (resource) edge[->] (match);
\end{tikzpicture}

### 2016-09-06 head.tex
改版

\author[label1]{Shengkai Chen}
\author[label1]{Shuiliang Fang}
% \address[label1]{ZJU}
% \address[label1]{Address One}
\address[label1]{Zhejiang University, Institute of manufacturing engineering and automation, Hangzhou City, Zhejiang Province, China}

% \fntext[label4]{Small city}

\begin{abstract}
In Cloud Manufacturing, individuals engage in manufacturing business through the well-designed platform framework, where provider provide manufacturing resource for demander to search and purchase it as product. This business model allows centralized management of distributed massive manufacturing resources, and could potentially reduce the idle rate of those resources.
However, in the manufacturing ecosystem constructed, the heterogeneity of resource's attribute like type, quality, price, processing velocity, leads tough taxonomy of these resources, and the chaotic operating mode, makes it hard to meet demander's need. Meantime, in order to enhance the cash flow rate, provider make decisions to enhance the use rate of their own resources.
The relationship among participants in this ecosystem become more complicated than that in normal manufacturing system, since the integrated advanced technologies within cloud environment makes it possible to let one individual make decisions depend on the surroundings and other's decisions. Hence, in this paper, we designed an original operation mode with 3 extension options for the cloud manufacturing ecosystem to support some decision makings for individuals and the platform operator.
With the help of Repast Simphony, we designed an agent-based model and experiment to simulate these operation modes with any combinations to validate the effectiveness of them. As the experiment result, incubation mode can help reduce the waiting of job and accelerate the process velocity of resources, outsourcing mode reduce the job queue length but not as much as incubation mode and requires more resources, metabolism mode require lower resources than the other modes and will slow resource process velocity a little. The combination of incubation and metabolism mode is ideal for platform operators to maintain the manufacturing ecosystem.
\end{abstract}

@@

\end{keyword}

>>>>

\author[add1]{Shengkai Chen}
\author[add1,add2]{Shuiliang Fang\corref{cor1}}
% \ead{me_fangsl@zju.edu.cn}
% \address[label1]{ZJU}
% \address[label1]{Address One}
\address[add1]{Key Laboratory of Advanced Manufacturing Technology of Zhejiang Province, College of Mechanical Engineering, Zhejiang University, Hangzhou , 310027, China}
\address[add2]{The State Key Laboratory of Fluid Power Transmission and Control, College of Mechanical Engineering, Zhejiang University, Hangzhou, 310027, China}
% \author[a,b,*]{Third Author}

% \address[a]{First affiliation, Address, City and Postcode, Country}
% \address[b]{Second affiliation, Address, City and Postcode, Country}
% \fntext[label4]{Small city}

\cortext[cor1]{Corresponding author. Tel.: +86-135-8880-3980; Email: me\_fangsl@zju.edu.cn}

\begin{abstract}
In cloud manufacturing, individuals engage in manufacturing business through the well-designed platform, where provider provide manufacturing resource for demander to search and purchase it. This business model allows platform operator to manage distributed massive manufacturing resources, which may help provider reduce the idle rate of their resources.
However, in such manufacturing ecosystem, the heterogeneity attribute of resource makes it tough to classify them, and the chaotic operation mode makes it hard to meet demander's need.
Cloud manufacturing ecosystem has more complicated relationship among individuals in it than that in normal manufacturing system, one individual can make decisions depend on the surroundings and others' with the help of integrated advanced technologies. Thus, in this paper, we designed an original operation mode with 3 extensions for the cloud manufacturing ecosystem to help describe some decision makings in individuals and the platform operator.
With the help of Repast Simphony, we designed an agent-based simulation model and an experiment to validate the effectiveness of these operation modes. The experiment result shows: with incubation mode, the job queue length is reduced and the resource idle rate is declined; with outsourcing mode, the job queue length is also reduced but not as much as that with incubation mode and more resource is required; with metabolism mode, lower resource is required than that with other modes and resource idle rate just rose up a little. The combination of incubation and metabolism mode is one ideal mode to maintain the manufacturing ecosystem with.
\end{abstract}

@@

\end{keyword}
% \belowfrontmatterskip0pt

### 2016-09-06 intro.tex
改版

% !TEX root = Eco-Model.tex
\section{Introduction}
With the emergence of cloud manufacturing, the relationship among participants in the manufacturing system become more complicated then ever before since every single ind

In this paper, we constructed a

proposed 3 operation modes as options for platform to operate with named metabolism mode, incubation mode and outsourcing mode.

>>>>

% !TEX root = Eco-Model.tex
\section{Introduction}
The relationship among individuals in cloud manufacturing system become more complicated than that in normal manufacturing system, since the integrated advanced technologies makes it possible to let one individual make decisions depend on the surroundings and others'. Demander prefer high quality performance while provider prefer high use rate of their resource, the cloud platform operator prefer lower amount of registered resource when dealing with almost arriving needs for an easier maintenance. These preferences stimulate the emergence of good service pattern that will lead to the evolution of manufacturing pattern in the cloud manufacturing ecosystem. Hence, it's important to identify good operation mode that help the evolution.

In this paper, we designed an original operation mode to describe the basic decision makings in cloud manufacturing ecosystem, then we proposed 3 extensions named metabolism mode, incubation mode and outsourcing mode. Finally, we deigned an experiment to validate these synthetic operation modes in an agent-based simulation method.

### 2016-09-06 result.tex
改版

Entities in the manufacturing ecosystem we designed above have these traits: \begin{inparaenum}[1)]
\item autonomous and self-directed, 
\item social, interacting with other entities, 
\item controlled by the environment, 
\item self-contained.
\end{inparaenum} They optimize their multi-objective decision makings to interact with others and the environment, hence, agent-based modeling and simulation(ABMS) technique\cite{Macal2009,north2007managing} is suitable for the study of the complex system. With the help of Repast Simphony\cite{North2013} package, we realized the ecosystem model and performed some experiments on it.

@@

We design experiments to validate incubation, outsourcing and metabolism mode \autoref{tab:grouping}, 10 datasets represent 10 types of orders, each of them contains 10 tasks with different configuration on 12 types of resources to perform with.

@@

\subsection{Result and analysis} % (fold)
\label{ssub:result_and_analysis}
All the experiments are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.  After bunch of experiments with different random seeds, we discovered some laws in operation mode. Take random seed 776189616 as example, we run the simulation for 6000 tick time and the experiment's results are displayed in \autoref{fig:out} and \autoref{tab:averagevalue},
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{Data/out.pdf}
    \caption{Observed variable change with time}
    \label{fig:out}
\end{figure}
\begin{table}[htbp]
    \caption{Average observed values}
    \label{tab:averagevalue}
    \centering
    \scriptsize
    \begin{tabular}{lccccc}
    \toprule
    \textbf{Mode} & $\bar N_T$ & $\bar N_F$ & $\bar N_P$ & $\bar N_R $ & $\bar Q$\\
    \midrule
    Mode 11 & 1159.36 &  1644.201 &  1177.601 &  2053.727 &  8.388\\
    Mode 21 & \textit{636.769} &  \textit{2031.215} &  \textbf{692.716} &  \textbf{1066.947} &  16.016\\
    Mode 31 & 779.413 &  1996.021 &  \textit{782.272} &  \textit{1203.748} &  15.174\\
    Mode 12 & 1439.831 &  1522.923 &  1797.883 &  2954.113 &  14.057\\
    Mode 22 & \textbf{343.444} &  \textbf{2464.407} &  1316.952 &  1957.226 &  \textit{20.251}\\
    Mode 32 & 1164.409 &  1907.011 &  1597.742 &  2428.155 &  \textbf{20.652}\\

    \bottomrule
    \end{tabular}
\end{table}
we find: \begin{inparaenum}[1)]
\item Most dotted lines are above the full lines with the same series in $N_R,N_P,N_T$ means that metabolism mode need lower number of provider and resource, with the price of higher number of queue length of the tasks in resources in the system to deal with the same amount of needs, except for Mode 22. Full lines are not much above dotted lines in $N_F$ means that task processing velocity will be a little slower with the metabolism, exception also appears in Mode 22. 
\item $L$ and $N_T$ both represent the queue length of jobs, triangle and square line turned lower in $L$ meas that incubation mode can help reduce the waiting of job, these two type of line above the circle line means the incubation mode do accelerate the processing velocity.
\item Triangle lines are a little above the square lines in $N_R,N_P,N_T$ means that outsourcing mode needs more resources to operate and can only reduce the waiting of job a little.
\item There is no big difference among all the 6 modes in rank change. Provider in metabolism mode will get lower rank value for they cannot stay in the system for long, the longer stay in the system, the higher rank value provider will get. Provider in Mode 11 even will not promote their rank value, which means that the metabolism rate is very fast without incubation mode.
\item Mode 22 is a very special mode that reached the balance in 6000 ticks, that the number of provider and resource changes little with time goes by. Because our experiment setting comply \autoref{eq:balance}, the coming need capacity velocity is less than the coming capacity, Mode 12,22,32 will finally reach balance in the long run theoretically, but the appearance of service-call and metabolism itself is full of uncertainty and it's hard to predict when other metabolism related mode will get the balance.
\item With the average data value shown in \autoref{tab:averagevalue}, metabolism with incubation but not with outsourcing mode is the easiest combine mode to maintain the system, resource will self-configured and controlled to justly meet the task need.
\end{inparaenum}

>>>>

Individuals in the manufacturing ecosystem are: \begin{inparaenum}[1)]
\item autonomous and self-directed, 
\item social, interacting with other entities, 
\item controlled by the environment, 
\item self-contained.
\end{inparaenum} They optimize their multi-objective decision makings to interact with others and the environment, hence, agent-based modeling and simulation(ABMS) technique\cite{Macal2009,north2007managing} is suitable for the study in such complex system. With the help of Repast Simphony\cite{North2013} package, we realized the ecosystem model and performed some experiments with it.

@@

We design experiments in groups to validate incubation, outsourcing and metabolism mode \autoref{tab:grouping}, 10 datasets represent 10 types of orders, each of them contains 10 tasks with different configuration on 12 types of resources to perform with.

@@

\subsection{Result and analysis} % (fold)
\label{ssub:result_and_analysis}
Experiment on each mode in one group are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.  After bunch of experiments with different random seeds, take random seed 776189616 as example, we run the simulation for 6000 tick time and the experiment's results are displayed in \autoref{fig:out} and \autoref{tab:averagevalue},
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{Data/out.pdf}
    \caption{Observed variable change with time}
    \label{fig:out}
\end{figure}
\begin{table}[htbp]
    \caption{Average observed values}
    \label{tab:averagevalue}
    \centering
    \scriptsize
    \begin{tabular}{lccccc}
    \toprule
    \textbf{Mode} & $\bar N_T$ & $\bar N_F$ & $\bar N_P$ & $\bar N_R $ & $\bar Q$\\
    \midrule
    Mode 11 & 1159.36 &  1644.201 &  1177.601 &  2053.727 &  8.388\\
    Mode 21 & \textit{636.769} &  \textit{2031.215} &  \textbf{692.716} &  \textbf{1066.947} &  16.016\\
    Mode 31 & 779.413 &  1996.021 &  \textit{782.272} &  \textit{1203.748} &  15.174\\
    Mode 12 & 1439.831 &  1522.923 &  1797.883 &  2954.113 &  14.057\\
    Mode 22 & \textbf{343.444} &  \textbf{2464.407} &  1316.952 &  1957.226 &  \textit{20.251}\\
    Mode 32 & 1164.409 &  1907.011 &  1597.742 &  2428.155 &  \textbf{20.652}\\

    \bottomrule
    \end{tabular}
\end{table}
we find: \begin{asparaenum}[1)]
\item Most dotted lines are above the full lines with the same series in $N_R,N_P,N_T$ means that metabolism mode need lower number of provider and resource, with the price of higher number of queue length of the tasks in resources in the system to deal with the same amount of needs, except for Mode 22. Full lines are not much above dotted lines in $N_F$ means that task finish rate will be a little lower with the metabolism, exception also appears in Mode 22. 
\item $L$ and $N_T$ both represent the job queue length, triangle and square line turned lower in $L$ meas that incubation mode can help reduce the waiting of job, these two type of line above the circle line means the incubation mode do reduce the resource idle rate.
\item Triangle lines are a little above the square lines in $N_R,N_P,N_T$ means that outsourcing mode needs more resources to operate and can only reduce the job queue length a little.
\item There is no big difference among all the 6 modes in rank change. Provider in metabolism mode will get lower rank value for they cannot stay in the system for a longer time to get higher rank value. Provider in Mode 11 even will not promote their rank value, which means that the metabolism rate is very fast if without incubation mode.
\item Mode 22 is a very special mode that reached the balance within 6000 ticks, that the number of provider and resource changes little with time goes by. Because our experiment setting comply \autoref{eq:balance}, the coming need capacity rate is lower than the coming capacity rate, Mode 12,22,32 will finally reach balance in the long run theoretically, but the appearance of service-call and metabolism mode itself is full of uncertainty, thus it's hard to predict when other metabolism related mode will reach the balance.
\item With the average data value shown in \autoref{tab:averagevalue}, metabolism with incubation but not with outsourcing mode is one ideal combine mode to maintain the system, resource will self-configured and controlled to justly meet the task need.
\end{asparaenum}

### 2016-09-06 review.tex
改版

% !TEX root = Eco-Model.tex
\section{Literature review and background} % (fold)
\label{sec:literature_review}
\subsection{Cloud manufacturing and its operation mode} % (fold)
\label{sub:cloud_manufacturing review}
% This definition is quite abstract and thus despite its corretness not very useful.

Review on 1. Cloud manufacturing mode (any) study 
2. res ser combination and decision making
3. rank and review ecosystem (system changing)
4. manufacturing system simulation

In cloud manufacturing context, centralized management for manufacturing services that encapsulated with distributed manufacturing resources can be realized by an appropriate business model\cite{Xu2012}

Currently, the literature review indicates that modular approaches and multi-layer architectures are the most common way to build the cloud manufacturing platform or system framework (\cite{Tao2012}\cite{Valilai2013}

Most recent studies like Wu et al.\cite{Wu2013} described the roles in Cloud Manufacturing as a tri-group model with:\begin{inparaenum}[1)]
\item Users/Customers,
\item Application providers and
\item Physical resource providers.
\end{inparaenum}

\subsection{Study background} % (fold)
\label{sub:background}

here we goes the terminology that will use in the following subsections within this section. all the related basic terms will in italics fonts.
\begin{itemize}
	\item order
	\item task correspond to capacity
	\item resource
	\item capacity is the function of a resource. like quantity
	\item service is the bundle of capacities. the proportion of the capacities.
	\item 
\end{itemize}

Combined with the background of the research problem and other scholars' previous study in cloud manufacturing, we proposed an improved framework that suits for cloud manufacturing environment

As defined above, Enterprise User is the special case of the User(short for Generalized User) that purely provides manufacturing services and the Customer User is similarly defined.

Hence, there is only two roles in the Ecosystem worth to be studied: User and Administrator, the proportion of user type could be adjusted as the runtime of the system goes by.

>>>>

% !TEX root = Eco-Model.tex
\section{Review on cloud manufacturing} % (fold)
\label{sec:literature_review}

% This definition is quite abstract and thus despite its corretness not very useful.

In cloud manufacturing context, platform operator can manage  manufacturing service that encapsulated with distributed manufacturing resources intensively with appropriate business model\cite{Xu2012}, modular approaches and multi-layer architectures are the most common approaches to build the cloud manufacturing platform or system framework\cite{Tao2012,Valilai2013}, Lv use list of views to depict this multi-layer architecture\cite{LvJuly312012-Aug.22012}.

Servitization is the key philosophy to operate cloud manufacturing\cite{li2010cloud}, service can be created statically which come along with provider\cite{Tao2012} or can be created dynamically according to task pattern, such method as `Multi-Composition for Each Task'\cite{Liu2013} that combines incompetent service into a whole, service can also be created by AI planning-based automatic composition framework\cite{OhJan.-March2008}.

Simulation approach have been widely use in manufacturing system on operations planning and scheduling, real-time control, operating polities, performance analysis\cite{Smith2003}. In operating policies field, scheduling policies can be tested with simulation performance under given machine conditions\cite{Sabuncuoglu2003}, machine
segmentation policies can be simulated in a combined MRP and Kanban production system\cite{Felberbauer9-12Dec.2012}. Mourtzis et al.\cite{Mourtzis2015} explored a series of simulation-based solutions in industrial practice and considered that research trends are Internet and cloud based situation.
